Semantic Frame Induction

### 2014-12-15 Paper/presentation.tex
Add ngrams slide.

%------------------------------------------------
\section{Semantic frames}
%------------------------------------------------

\begin{frame}
  \frametitle{Semantic frames}
  An example\\
  \vspace{10pt}
\begin{tabular}{|l|}
  \hline
  \textit{\small predicate:\normalsize}~~~Transaction\\
  \hline
  \hline
  \textit{\small role 1:\normalsize}~~~ baker\\
  \textit{\small role 2:\normalsize}~~~ Alice\\
  \textit{\small role 3:\normalsize}~~~ bread\\
  \hline
\end{tabular}\\
\vfill
\begin{itemize}
\item Alice buys a bread from the baker
\item The baker sells Alice a bread
  \end{itemize}
\end{frame}

@@

>>>>

%------------------------------------------------
\section{Semantic Frames}
%------------------------------------------------

\begin{frame}
  \frametitle{Semantic Frames}
  \begin{itemize}
  \item Frame semantics -- Charles J. Fillmore (1976).
  \item A semantic frame is ``a description of a type of event, relation, 
  or entity and the participants in it.'' (Framenet)
  \item There is no mapping between frames and verbs.
  \end{itemize}
  An example:\\
  \vspace{10pt}
\begin{tabular}{|l|}
  \hline
  \textit{\small predicate:\normalsize}~~~Transaction\\
  \hline
  \hline
  \textit{\small role 1:\normalsize}~~~ baker\\
  \textit{\small role 2:\normalsize}~~~ Alice\\
  \textit{\small role 3:\normalsize}~~~ bread\\
  \hline
\end{tabular}\\
\vfill
\begin{itemize}
\item Alice buys a bread from the baker
\item The baker sells Alice a bread
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Google Syntactic-Ngrams}
  \begin{itemize}
  \item A syntactic-ngram is a $k$-word rooted subtree for some sentence. 
  \item Google ngrams come from a corpus of 3.5 million English books.
  \item We trimmed the ``verb args'' dataset to consider only subject-verb-object triples (VSO's).
  \item The dataset contains 1,629,120 unique VSO's with a total of 96,245,401 by count.
  \item In our final results we may only use the most common \%20 of these...
  \end{itemize}
